Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-04-30 article-models-tt.tex
added stuff to intro of 4.3

Apart from the empty context, there will indeed be an empty family and a term
of the empty family (which will be deemed unique). But context extension will
not have an explicit action `at the level of families' since extension
is used to define higher families and the action would have to be trivial
anyway. The operations of weakening and substitution are actually introduced
by four inference rules and the identity terms by one.

>>>>

Apart from the empty context, there will indeed be an empty family and a term
of the empty family (which will be deemed unique). But extension will
not have an explicit action `at the level of families' since extension
is used to define higher families and the action would have to be trivial
anyway. The empty context and extension provide the essentials of the rest of
the theory in the sense that higher families are families over extensions,
contexts are families over the empty context and the `action on families' of
any operation applied to families over the empty context is the same as the
original operation. Thus, when we have introduced the operations of weakening
and substitution we will see that they also have an `action on the terms of 
contexts'. We will state the relevant judgmental equality rules for the empty
context in this section rather than in the next, since they are required to
state that the action on families of an operation is compatible with the
original operation.
